---
title: "Elk_LULC_Results_May2021"
author: "Wenjing"
date: "5/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Intro
```{r intro, echo = FALSE, message = FALSE}
library(sf)
library(tidyverse)
library(hrbrthemes)
library(wesanderson)

setwd("/Users/Mushy 1/Google Drive (wenjing.xu@berkeley.edu)/RESEARCH/Elk/GYE_ELK_LandUse")
data <- read_csv("./result/results_0716.csv") %>% mutate( Range = factor(Range, levels = c("winter", "migration", "summer")))
sp <- read_sf("./data_clean/seasonalRanges/herdSeasonsUpdatedProj.shp") %>% rename(Herd = herd, Range = season)
```

We derived summer range, winter range, and migration corridor for `r length(unique(data$Herd))` herds.

We have analyzed below layers:
```{r intro2, echo = FALSE, message = FALSE}
unique(data$Layer)
```

## graphs
### Home range area 
area of home range, order by total area
```{r area1, echo=FALSE, message = FALSE}
sp <- sp %>% mutate (area = st_area(sp))
sp1 <- sp %>% group_by (Herd) %>% summarise(area = sum(area)) %>% arrange(area) %>% mutate(Herd=factor(Herd, levels=Herd))
sp2 <- sp %>% mutate (Herd = factor(Herd, levels = levels(sp1$Herd)))
st_geometry(sp2) <- NULL

sp2 %>% mutate (Range = factor(Range, levels = c("winter", "migration", "summer"))) %>%
  ggplot(aes(x=Herd, y= as.numeric(area)/1000000, fill = Range)) +
  geom_bar(stat = "identity") +  
  scale_fill_manual(values=wes_palette("Moonrise3", 3, "continuous")) +
  theme_ipsum(base_size = 12, axis_text_size = 10) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "HR area (km2)") +
  theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8))
```


### Land ownership
Percentage of land ownership, order by %private land in winter.  
```{r land_ownership, echo=FALSE}
data1 <- data %>% filter(Layer == "Land_ownership") %>% mutate (Category = factor(Category, levels = c("OTHER_FED","ST", "BLM", "NPS", "USFS", "PVT"))) 
# update herd order 
data11 <- data1 %>% filter(Range == "winter", Category == "PVT") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data1 <- data1 %>% mutate (Herd = factor(Herd, levels = levels(data11$Herd)))

tiff('/Users/Mushy 1/Google Drive (wenjing.xu@berkeley.edu)/RESEARCH/Elk/GYE_ELK_LandUse/result/GYE_graph_cmpts/ownership_color.tiff', units="in", width=11, height=6, res=300, compression = 'lzw')
data1 %>%
  ggplot(aes(x=Herd, y=Value, fill = Category)) +
  geom_bar(position = "stack", stat = "identity") +  
  scale_fill_manual(values=wes_palette("GrandBudapest2", 6, "continuous")) +
  #scale_fill_grey(start = 0.3, end = 0.7) +
  theme_ipsum(base_size = 12, axis_text_size = 7) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "Percentage") + 
  theme(axis.title.x = element_blank()) +
  theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
dev.off()
```

### Protected status
Percentage of protected status (protected v.s. not protected), order by % un-protected in winter. 
```{r Protected_status1, echo=FALSE}
data21 <- data %>% filter(Layer == "Protected_status") %>% 
  mutate(Category = ifelse( Category == "NOT_PROTECTED", Category, "PROTECTED")) %>%
  mutate(Category = factor(Category, levels = c("PROTECTED", "NOT_PROTECTED")))
data211 <- data21 %>% filter(Range == "winter", Category == "NOT_PROTECTED") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data21 <- data21 %>% mutate (Herd = factor(Herd, levels = levels(data211$Herd)))

data21 %>%
  ggplot(aes(x=Herd, y=Value, fill = Category)) +
  geom_bar(position = "stack", stat = "identity") +  
  scale_fill_manual(values=wes_palette("Chevalier1")) +
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "Percentage") + 
  theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```

Percentage of protected status by public conservation area v.s. easement v.s. unprotected, order by % un-protected in winter. 
```{r Protected_status2, echo=FALSE}
data22 <- data %>% filter(Layer == "Protected_status") %>% 
  mutate(Category = ifelse( (Category %in% c("e1", "e2", "e3", "e4")), "EASEMENT", 
                            ifelse(Category == "NOT_PROTECTED", Category, "PA"))) %>%
  mutate(Category = factor(Category, levels = c("PA", "EASEMENT", "NOT_PROTECTED")))
data221 <- data22 %>% filter(Range == "winter", Category == "NOT_PROTECTED") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data22 <- data22 %>% mutate (Herd = factor(Herd, levels = levels(data221$Herd)))

tiff('/Users/Mushy 1/Google Drive (wenjing.xu@berkeley.edu)/RESEARCH/Elk/GYE_ELK_LandUse/result/GYE_graph_cmpts/protection_color.tiff', units="in", width=11, height=6, res=300, compression = 'lzw')
data22 %>%
  ggplot(aes(x=Herd, y=Value, fill = Category)) +
  geom_bar(position = "stack", stat = "identity") +  
  scale_fill_manual(values=wes_palette("Chevalier1")) +
  #scale_fill_grey(start = 0.4, end = 0.75) +
  theme_ipsum(base_size = 12, axis_text_size = 7) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "Percentage") + 
  theme(axis.title.x = element_blank()) +
  theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
dev.off()
```

Percentage of protected status by protected level regardless of easement or public, order by % un-protected in winter. 1 - 4 represent protect level from high to low.

```{r Protected_status3, echo=FALSE}
data23 <- data %>% filter(Layer == "Protected_status") %>% 
  mutate(Category = ifelse( Category == "e1", "1", 
                            ifelse(Category == "e2", "2", 
                                   ifelse(Category == "e3", "3", 
                                          ifelse(Category == "e4", "4", Category))))) %>%
  mutate(Category = factor(Category, levels = c("1", "2", "3", "4", "NOT_PROTECTED")))
data231 <- data23 %>% filter(Range == "winter", Category == "NOT_PROTECTED") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data23 <- data23 %>% mutate (Herd = factor(Herd, levels = levels(data231$Herd)))

tiff('/Users/Mushy 1/Google Drive (wenjing.xu@berkeley.edu)/RESEARCH/Elk/GYE_ELK_LandUse/result/GYE_graph_cmpts/supp-protection_level_color.tiff', units="in", width=11, height=6, res=300, compression = 'lzw')
data23 %>%
  ggplot(aes(x=Herd, y=Value, fill = Category)) +
  geom_bar(position = "stack", stat = "identity") +  
  scale_fill_manual(values=wes_palette("Chevalier1", 5, "continuous")) +
  #scale_fill_grey(start = 0.4, end = 0.75) +
  theme_ipsum(base_size = 12, axis_text_size = 7) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "Percentage") + 
  theme(axis.title.x = element_blank()) +
  theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
dev.off()
```

### number of private owners
```{r OWNERS, echo=FALSE}
data8 <- data %>% filter(Layer == "Private_owners") 
data81 <- data8 %>% filter(Range == "winter") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data8 <- data8 %>% mutate (Herd = factor(Herd, levels = levels(data81$Herd)))

data8 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#DE7994") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "# of owners") + 
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```

### Agriculture 
```{r Ag, echo=FALSE}
data3 <- data %>% filter(Layer == "Proportion_ag") 
data31 <- data3 %>% filter(Range == "winter") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data3 <- data3 %>% mutate (Herd = factor(Herd, levels = levels(data31$Herd)))

data3 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#EC9F05") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "Percentage") + 
  #theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```

### Engergy 
max energy density (what is the unit? what energy type?)

```{r Engergy1, echo=FALSE}
data4 <- data %>% filter(Layer == "energy", Category == "max") 
data41 <- data4 %>% filter(Range == "winter", Category == "max") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data4 <- data4 %>% mutate (Herd = factor(Herd, levels = levels(data41$Herd)))

data4 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#626c66") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "Max energy density (what is the unit?)") + 
  #theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```
mean energy density (what is the unit? what energy type?)

```{r Engergy2, echo=FALSE}
data4 <- data %>% filter(Layer == "energy", Category == "mean") 
data41 <- data4 %>% filter(Range == "winter", Category == "mean") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data4 <- data4 %>% mutate (Herd = factor(Herd, levels = levels(data41$Herd)))

data4 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#626c66") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "Mean energy density (what is the unit?)") + 
  #theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```



### Current building density
```{r Building density1, echo=FALSE}
data5 <- data %>% filter(Layer == "currentBuildings", Category == "max") 
data51 <- data5 %>% filter(Range == "winter", Category == "max") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data5 <- data5 %>% mutate (Herd = factor(Herd, levels = levels(data51$Herd)))

data5 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#E1CA96") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "max building density (#/km2)") + 
  #theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```
```{r Building density2, echo=FALSE}
data5 <- data %>% filter(Layer == "currentBuildings", Category == "mean") 
data51 <- data5 %>% filter(Range == "winter", Category == "mean") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data5 <- data5 %>% mutate (Herd = factor(Herd, levels = levels(data51$Herd)))

data5 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#E1CA96") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "mean building density (#/km2)") + 
  #theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```

```{r Road1, echo=FALSE}
data6 <- data %>% filter(Layer == "allRoads", Category == "max") 
data61 <- data6 %>% filter(Range == "winter", Category == "max") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data6 <- data6 %>% mutate (Herd = factor(Herd, levels = levels(data61$Herd)))

data6 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#7F636E") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "max road density (km/km2)") + 
  #theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```

```{r Road2, echo=FALSE}
data6 <- data %>% filter(Layer == "allRoads", Category == "mean") 
data61 <- data6 %>% filter(Range == "winter", Category == "mean") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data6 <- data6 %>% mutate (Herd = factor(Herd, levels = levels(data61$Herd)))

data6 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#7F636E") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "mean road density (km/km2)") + 
  #theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```

Interstate only road density - 

```{r Road3, echo=FALSE}
data6 <- data %>% filter(Layer == "interstateOnly", Category == "max") 
data61 <- data6 %>% filter(Range == "winter", Category == "max") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data6 <- data6 %>% mutate (Herd = factor(Herd, levels = levels(data61$Herd)))

data6 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#55868C") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "max interstate density (km/km2)") + 
  #theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```


```{r Road4, echo=FALSE}
data6 <- data %>% filter(Layer == "interstateOnly", Category == "mean") 
data61 <- data6 %>% filter(Range == "winter", Category == "mean") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data6 <- data6 %>% mutate (Herd = factor(Herd, levels = levels(data61$Herd)))

data6 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#55868c") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "mean interstate density (km/km2)") + 
  #theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```

### Fence density 

```{r fence1, echo=FALSE}
data7 <- data %>% filter(Layer == "fence", Category == "max") 
data71 <- data7 %>% filter(Range == "winter", Category == "max") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data7 <- data7 %>% mutate (Herd = factor(Herd, levels = levels(data71$Herd)))

data7 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#a588b3") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "max fence density (km/km2)") + 
  #theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```


```{r fence2, echo=FALSE}
data7 <- data %>% filter(Layer == "fence", Category == "mean") 
data71 <- data7 %>% filter(Range == "winter", Category == "mean") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data7 <- data7 %>% mutate (Herd = factor(Herd, levels = levels(data71$Herd)))

data7 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#a588b3") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "mean fence density (km/km2)") + 
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```

### livestock 
```{r livestock mean, echo=FALSE}
data9 <- data %>% filter(Layer == "allLivestock", Category == "mean") 
data91 <- data9 %>% filter(Range == "winter") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data9 <- data9 %>% mutate (Herd = factor(Herd, levels = levels(data91$Herd)))

data9 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#83B5D1") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "mean livestock denstiy(count/km2)") + 
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```

```{r livestock max, echo=FALSE}
data9 <- data %>% filter(Layer == "allLivestock", Category == "max") 
data92 <- data9 %>% filter(Range == "winter") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data9 <- data9 %>% mutate (Herd = factor(Herd, levels = levels(data92$Herd)))

data9 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#83B5D1") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "max livestock density (km/km2)") + 
  #theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_blank(), legend.text = element_text(size = 8)) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```

```{r cattle mean, echo=FALSE}
data9 <- data %>% filter(Layer == "cattle", Category == "mean") 
data93 <- data9 %>% filter(Range == "winter") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data9 <- data9 %>% mutate (Herd = factor(Herd, levels = levels(data93$Herd)))

data9 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#83B5D1") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "mean cattle equivalent denstiy (count/km2)") + 
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```

```{r cattle max, echo=FALSE}
data9 <- data %>% filter(Layer == "cattle", Category == "max") 
data94 <- data9 %>% filter(Range == "winter") %>% arrange(-Value) %>% mutate(Herd=factor(Herd, levels=Herd))
data9 <- data9 %>% mutate (Herd = factor(Herd, levels = levels(data94$Herd)))

data9 %>%
  ggplot(aes(x=Herd, y=Value)) +
  geom_bar(position = "stack", stat = "identity", fill = "#83B5D1") +  
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs (y = "max cattle equivalent denstiy (count/km2)") + 
  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
  facet_wrap(vars(Range))
```

## maps
### percent protected 
```{r protected map, echo=FALSE}
data2 <- data21 %>% filter(Category == "PROTECTED") %>% group_by(Herd, Range) %>% summarise(Value = sum(Value))
sp2 <- sp %>% left_join(data2)

sp2 %>%
  ggplot() +
  geom_sf(aes(fill = Value), size = 0.01) +
  scale_fill_gradient(name = "percent protected  ", low = "#d1d1d1", high= "#065d46", na.value = NA) +
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.5, 'cm'), legend.title = element_text(size = 10), legend.text = element_text(size = 8)) 
```

### by # of private owners 
```{r owner map, echo=FALSE}
sp8 <- sp %>% left_join(data8)

tiff('/Users/Mushy 1/Google Drive (wenjing.xu@berkeley.edu)/RESEARCH/Elk/GYE_ELK_LandUse/result/GYE_graph_cmpts/map_owner_no_grey.tiff', units="in", width=11, height=6, res=300, compression = 'lzw')
sp8 %>%
  ggplot() +
  geom_sf(aes(fill = Value), size = 0.01) +
  coord_sf(datum = NA) +
  scale_fill_gradient(name = "owner#", low = "#e6e6e6", high= "#3d3d3d", na.value = NA) +
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_text(size = 10), legend.text = element_text(size = 8)) 
dev.off()
summary(sp8$Value)
```

## %zoned
```{r zoning map, echo=FALSE}
data0 <- data %>% filter(Layer == "zoning", Category == "percentZoned") 
sp0 <- sp %>% left_join(data0)

tiff('/Users/Mushy 1/Google Drive (wenjing.xu@berkeley.edu)/RESEARCH/Elk/GYE_ELK_LandUse/result/GYE_graph_cmpts/map_zone_0-668.tiff', units="in", width=11, height=6, res=300, compression = 'lzw')
sp0 %>%
  ggplot() +
  geom_sf(aes(fill = Value), size = 0.01) +
  coord_sf(datum = NA) +
  scale_fill_gradient(name = "% zoned", low = "#ededed", high= "#3d3d3d", na.value = NA) +
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_text(size = 10), legend.text = element_text(size = 8)) 
dev.off()
summary(sp0$Value)
```

### by percent ag 
```{r Ag map, echo=FALSE}
data3 <- data %>% filter(Layer == "Proportion_ag") 
sp3 <- sp %>% left_join(data3)

sp3 %>%
  ggplot() +
  geom_sf(aes(fill = Value), size = 0.01) +
  scale_fill_gradient(name = "percent ag  ", low = "#E7D9D1", high= "#DE9400", na.value = NA) +
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_text(size = 10), legend.text = element_text(size = 8)) 
```

### by mean ernergy density
```{r energy map, echo=FALSE}
data4 <- data %>% filter(Layer == "energy", Category == "mean") 
sp4 <- sp %>% left_join(data4)

tiff('/Users/Mushy 1/Google Drive (wenjing.xu@berkeley.edu)/RESEARCH/Elk/GYE_ELK_LandUse/result/GYE_graph_cmpts/energy_0-0626.tiff', units="in", width=11, height=6, res=300, compression = 'lzw')
sp4 %>%
  ggplot() +
  geom_sf(aes(fill = Value), size = 0.01) +
  coord_sf(datum = NA) +
  scale_fill_gradient(name = "energy density  ", low = "#ededed", high= "#3d3d3d", na.value = NA) +
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_text(size = 10), legend.text = element_text(size = 8)) 
dev.off()
summary(sp4$Value)
```

### by mean road density 
```{r road map, echo=FALSE}
data5 <- data %>% filter(Layer == "allRoads", Category == "mean") 
sp5 <- sp %>% left_join(data5)

sp5 %>%
  ggplot() +
  geom_sf(aes(fill = Value), size = 0.01) +
  scale_fill_gradient(name = "road density /km2  ", low = "#D9D3D3", high= "#85264c", na.value = NA) +
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_text(size = 10), legend.text = element_text(size = 8)) 
```

```{r road map2, echo=FALSE}
data51 <- data %>% filter(Layer == "interstateOnly", Category == "mean") 
sp51 <- sp %>% left_join(data51)

sp51 %>%
  ggplot() +
  geom_sf(aes(fill = Value), size = 0.01) +
  scale_fill_gradient(name = "interstate density /km2  ", low = "#bfcbcc", high= "#276c75", na.value = NA) +
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.5, 'cm'), legend.title = element_text(size = 10), legend.text = element_text(size = 8)) 
```


### by mean fence density 
```{r fence map, echo=FALSE}
data6 <- data %>% filter(Layer == "fence", Category == "mean") 
sp6 <- sp %>% left_join(data6)

tiff('/Users/Mushy 1/Google Drive (wenjing.xu@berkeley.edu)/RESEARCH/Elk/GYE_ELK_LandUse/result/GYE_graph_cmpts/fence_005-295.tiff', units="in", width=11, height=6, res=300, compression = 'lzw')
sp6 %>%
  ggplot() +
  geom_sf(aes(fill = Value), size = 0.01) +
  coord_sf(datum = NA) +
  scale_fill_gradient(name = "fence density /km2 ", low = "#ededed", high= "#1c1c1c", na.value = NA) +
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_text(size = 10), legend.text = element_text(size = 8)) 
dev.off()
summary(sp6$Value)
```


### by mean cattle equivalent density 
```{r cattle map, echo=FALSE}
data9 <- data %>% filter(Layer == "cattle", Category == "mean") 
sp9 <- sp %>% left_join(data9)
summary(sp9$Value)

tiff('/Users/Mushy 1/Google Drive (wenjing.xu@berkeley.edu)/RESEARCH/Elk/GYE_ELK_LandUse/result/GYE_graph_cmpts/cattle_0-601.tiff', units="in", width=11, height=6, res=300, compression = 'lzw')
sp9 %>%
  ggplot() +
  geom_sf(aes(fill = Value), size = 0.01) +
  coord_sf(datum = NA) +
  scale_fill_gradient(name = "# cattle", low = "#ededed", high= "#3d3d3d", na.value = NA) +
  theme_ipsum(base_size = 12, axis_text_size = 5) +
  theme(legend.position="bottom", legend.direction = "horizontal", legend.key.size = unit(0.3, 'cm'), legend.title = element_text(size = 10), legend.text = element_text(size = 8)) 
dev.off()
```
